Matching bullets

### 2015-11-17 imaging-paper.Rnw
manual match

To improve upon the previous algorithm, the first step must be to eliminate the grooves from the images under the assumption that they do not contain relevant information for determining a match. Fortunately, the location and appearance of the grooves in these 2d plots is quite consistent. Because a bullet is scanned groove to groove, the groove should appear within approximately scan points from each end. That is, on y coordinate system ranging from 0 to 1000 as these images, are, the grooves will appear between $y \in \{0, 100\}$ and $y \in \{900, 1000\}$. Hence, the algorith for removing the grooves can be described as follows:

@@

\section{Application}

>>>>

To improve upon the previous algorithm, the first step must be to eliminate the grooves from the images under the assumption that they do not contain relevant information for determining a match. Fortunately, the location and appearance of the grooves in these 2d plots is quite consistent. Because a bullet is scanned groove to groove, the groove should appear within approximately scan points from each end. That is, on y coordinate system ranging from 0 to 1000 as these images, are, the grooves will appear between $y \in \{0, 100\}$ and $y \in \{900, 1000\}$. Hence, the algorithm for removing the grooves can be described as follows:

@@

\begin{figure}
\includegraphics[width=\textwidth]{images/side-by-side-manual-match.png}
\caption{\label{fig:manualmatch}\hh{Manually adjusted side-by-side comparison of two lands from different bullets.}}
\end{figure}
\section{Application}
